### 2020-03-10 document/manuscript-out.tex
Travis build: 125

@@

@@

>>>>

\subsubsection{Proposed subsections and
content}\label{proposed-subsections-and-content}

The subsections will be based on the findings about the status of open
science in Kenya.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Resources to support open science are insufficient. The resources
  include:
\end{enumerate}

\begin{itemize}
\tightlist
\item
  ICT infrastructure. KENET provides infrastructure for open science
  training.
\item
  Institutional repositories. Universities and Research institutes have
  repositories to store publications. Also repositories to store
  research data. Do all institutions have these repositories?
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  Lacking policies and incentives from the government, local funders and
  institutions. These policies and incentives lack in open science
  practices such as:
\end{enumerate}

\begin{itemize}
\tightlist
\item
  Research data management. Apart from
  \href{https://cgspace.cgiar.org/handle/10568/63496}{ILRI's data
  management policy}, do other institutions have these policies?
\item
  Open access publishing
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  Limited training on Open Science. Awareness on Open Science has
  previously been through:
\end{enumerate}

\begin{itemize}
\tightlist
\item
  Open access week in universities. (Do research institutions
  participate in Open Access week?)
\item
  Workshops such as OpenScienceKE Workshop in 2018
\item
  Others?
\end{itemize}

@@

\subsubsection{Proposed title and
content}\label{proposed-title-and-content}

The title here should indicate whether \emph{Kenyan researchers are
embracing open science practices} as per the findings of the Data Mining
team. This section's discussion may therefore focus on supporting this
claim based on:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The publishing trend of Kenyan researchers. The trend indicates that
  open access publishing is popular. The popular journals where Kenyan
  researcher publish are open access.
\item
  Pre-prints. \textbf{\emph{more work needed here to find out whether
  they have embraced preprints and if so, who is driving the adoption?}}
\item
  Open data and Code.
  \textbf{\emph{\href{https://github.com/BioinfoNet/Data-mining/issues/11}{This
  is yet to be completed}. We need to find out whether Kenyan authors
  are making the data and code available and accessible, and whether
  they are adhering to the FAIR principles}}
\item
  Collaboration trends. Are Kenyan authors collaborating from within or
  without? This milestone is still pending. 5 What else?
\end{enumerate}

@@

\subsubsection{Proposed content of
Section}\label{proposed-content-of-section}

\begin{itemize}
\tightlist
\item
  Low cost open access publishing is available.
\end{itemize}

Here our discussion will indicate that there are publishers offering
waivers and subsidies for developing countries (low income and lower
middle income countries). Waiver is either Full or 50\% of the APCs.
Sometimes, waivers are offered on a case-by-case basis. The resource
created will create awareness on where to publish at low cost in an open
access way.
